What paradigms can webcam eye-tracking be used for? Attempted replications of five ``classic'' cognitive science experiments

### 2024-10-10 manuscript.Rmd
little fixes to knit the pdf
Responding to Arial's qs

affiliation:
  - id: '1'
    institution: Cognitive Science Department, Vassar College
  - id: '2'
    institution: Department of Cognitive & Information Science, University of California,
      Merced
  - id: '3'
    institution: Psychology Department, Macalester College
  - id: '4'
    institution: Department of Psychology & Neuroscience, Boston College

@@

### Apparatus
HELP

## Results
```{r E1-analysis-JoshH-lab, child = 'E1-analysis-comparison-to-Hartshorne.Rmd'}

@@

In sum, the `webgazer` plug-in for `jsPsych` can be fruitfully used to conduct a variety of cognitive science experiments on the web, provided the limitations of the methodology are carefully considered. Studies with ROIs that take up half or a quarter of the participant's display, which encompasses a large number of common paradigms, are very likely to be successful, even when testing questions related to the timecourse of processing. However, the smaller the ROIs, the more important the calibration becomes. For instance, studies with four ROIs may want to exclude data from participants with less than 75% validation accuracy, whereas studies using two halves of the display as ROIs may not need to be so conservative. Studies with smaller ROIs (see Experiment 1) may not be appropriate for webcam eye-tracking in its current form.

>>>>

affiliation:
  - id: '1'
    institution: Cognitive Science Department, Vassar College
  - id: '2'
    institution: Department of Cognitive & Information Science, University of California,
      Merced
  - id: '3'
    institution: Psychology Department, Macalester College
  - id: '4'
    institution: Department of Communication Sciences and Disorders, MGH Institute of Health Professions

authornote: |
  Partial funding for JKH's contributions was provided by NSF2436092. The authors declares no competing interests.

@@

### Apparatus
Subjects were tested on a MacIntosh laptop using the built-in Webcam. The study was run in Chrome using the same code as Exp. 1a.

## Results
```{r E1-analysis-JoshH-lab, child = 'group-a/E1-analysis-comparison-to-Hartshorne.Rmd'}

@@

In sum, the `webgazer` plug-in for `jsPsych` can be fruitfully used to conduct a variety of cognitive science experiments on the web, provided the limitations of the methodology are carefully considered.

## Lessons and Questions

The findings above suggest a few lessons for researchers wishing to conduct eyetracking studies with a Webcam, as well as highlighting a few important methodological questions that need to be addressed going forward.

First, it appears that current technology is sufficient for studies with relatively large ROIs of half or a quarter of the screen. While this encompasses a large number of common paradigms, it does not cover all of them, even within the Visual World Paradigm. It is possible that even with current technology reasonable sensitivity could be achieved with slightly smaller ROIs, but it will require more systematic investigation to determine what exactly is feasible. Likewise, improving the technology may result in better precision. However, we note that anecdotally, humans -- who have been shaped by evolution to be exquisitely atuned to eyegaze -- have difficulty determining direction with more precision than quadrants. (This observation is based on the experience of many developmental psychology labs that used human coders to identify eyegaze direction frame-by-frame in videos of research subjects' faces.)

Note also that while ROIs the size of quadrants are feasible, good calibration is important. Based on the results above, researchers using such paradigms may want to exclude data from participants with less than 75% validation accuracy, whereas studies using two halves of the display as ROIs may not need to be so conservative.

Second, researchers need to take care with timing accuracy. Running studies on modern computers requires synchronizing multiple clocks, something that does not happen automatically. Failure to synchronize can result in substantial inaccuracies [@slim2022moving]. As indicated by the current work, the current jsPsych implementation of WebGazer.js has reasonably good timing synchronization. We recommend that future researchers use jsPsych or another package with similar documented precision.

Third, it is true for any eyetracker that precise data depends on good callibration, and good callibration depends in part on lighting and background. We suspect that it is possible to give subjects automated feedback on how to improve their own calibration, which could result in higher-quality data and fewer subject exclusions based on poor calibration.
